Accuracy and precision of zero-heat-flux temperature measurements with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System

### 2020-05-08 manuscript/manuscript.Rmd
R1 submitted

Code availability: All data used in the meta-analyses is available [here](https://github.com/awconway/zhf-review) and archived [here]().

>>>>

Code availability: All data used in the meta-analyses is available [here](https://github.com/awconway/zhf-review) and archived [here](https://doi.org/10.5281/zenodo.3817610).
